---
title: "Week 2 Exercises"
author:
date:
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

## 5.2.4 Exercise

#### 1: Find all flights that

(1) Had an arrival delay of two or more hours
(2) Flew to Houston (IAH or HOU)
(3) Were operated by United, American, or Delta
(4) Departed in summer (July, August, and September)
(5) Arrived more than two hours late, but didn’t leave late
(6) Were delayed by at least an hour, but made up over 30 minutes in flight
(7) Departed between midnight and 6am (inclusive)

## 5.3.1 Exercises
#### 1: How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).

#### 3: Sort flights to find the fastest (highest speed) flights.

## 5.4.1 Exercise
#### 4: Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("TIME"))
```

## 5.5.2 Exercise
#### 5: What does 1:3 + 1:10 return? Why?

## 5.6.7 Exercise
#### Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))

